Planck and the Extra-terrestrials\\ or what the new SI means for astronomy

### 2020-04-08 spg/main.tex
editing

Optical magnitude.  Photon flux on logarithmic wavelength scale.
Rounds nicely.  eNot to be confused with seismological magnitudes.

>>>>

In the astronomy literature one finds many named units (\AA ngström,
gauss, jansky) that are simply powers of 10 times SI units, which need
not detain us here.  There are also parody units such as
$\!\unit{gallon}\unit{Mpc}^{-1}$ for cross-sections (it depends on the
type of gallon, but is about a kilobarn), which would need an article
to themselves.  The only remaining unit that needs discussing is the
optical magnitude scale.  Optical magnitudes are a measure of
brightness going back to classical times, but like other units they
have been progressively redefined, and are now considered
SI-traceable.  A zero-magnitude source (such as the star Vega)
corresponds to a flux of roughly $10^{10}$ photons
$\!\unit{m}^{-2}\unit{s}$ in a typical spectral band.  More precisely,
zero magnitude is $5.480 \times10^{10}$ photons
$\!\unit{m}^{-2}\unit{s}$ per logarithmic spectral interval, with each
5~mag being 100 times fainter.  Since modern optical cameras are
invariably counters of photons, it makes sense to simply use photon
fluxes rather than optical magnitudes, with ``rounded'' magnitudes
used for historical comprehension.
